On semidefinite-representable sets over valued fields

### 2025-12-23 issac_biblatex_tentative/paper_CNV.tex
end sec 3

Thanks to Definition \ref{smith_nf}, (the matrix of) $f$ can be written $f = Q^{-1} \Delta P$
with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
and $\Delta = \mathrm{SNF}(f)\in \allmat_{n,m}(K)$ of the form $\diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r})$
  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for $\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$

By Lemma \ref{lem:DIaut} DI${}_{aut}$,
$P(\PP)$ is a polyhedron defined only by inequalities.

Let $\Qc= P(\PP)$
We now prove that $\Delta (\Qc)$ is a polyhedron.
One can write that $\Delta$ is the composition
of the immersion 
$K^r \rightarrow K^n$
$(x_1,\dots,x_r)\mapsto (x_1,\dots,x_r,0,\dots,0),$ 
 the diagonal invertible mapping
$K^l \rightarrow K^l$,
$(x_1,\dots,x_r)\mapsto (\delta_1 x_1,\dots,\delta_r x_r)$,
and the projections
$(x_1,\dots,x_{r+1})\mapsto (x_1,\dots,x_{r}),$
 $(x_1,\dots,x_{r+2})\mapsto (x_1,\dots,x_{r+1}),$
 $\dots,$
 $(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
 Thus, thanks to Lemmas \ref{lem:DIimm} DI${}_{imm}$, \ref{lem:DIproj} DI${}_{proj}$ and \ref{lem:DIaut} DI${}_{aut}$, $\Delta (\Qc)$ is a polyhedron.
 One can note that it is only when applying the immersion as the last mapping in the composition chain that equalities are needed to define the last polyhedron.

Finally, thanks to Lemma \ref{lem:DIaut} DI${}_{aut}$,
$Q^{-1} \left( \Delta (\Qc) \right)$ is a polyhedron.
This concludes the proof.
\end{proof}

We can generalize from linear mappings to affine mappings.
\begin{proposition}[DI${}_i$]
Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron in $K^n$ defined only by inequalities.
Then $f(\PP)$ is a polyhedron. \label{prop:DIi}
\end{proposition}
\begin{proof}
Let $P \in K^m$. One can see by immediate change of variables that $\Qc$ is a polyhedron in $K^m$ if and only if
$\Qc+P$ is a polyhedron in $K^m$.
Consequently, translating by $-f(O)$ in the codomain, one can reduce
to the case of Proposition \ref{prop:DIl}   DI${}_l$.
\end{proof}

@@

\begin{proof}[Proof of Theorem \ref{theo:DI} DI]
Here, $f : K^n \to K^m$ is an affine map and $\PP$ a polyhedron in $K^n.$
Let us write $\PP = \PP_I \cap \PP_E$
with $\PP_I \coloneq \left\lbrace X \in K^n,  AX+B \geq 0 \right\rbrace$
and $\PP_E \coloneq \left\lbrace X \in K^n,  CX+D=0 \right\rbrace = P + \overrightarrow{\PP_E}.$ 
Then $f(\PP) = f_{\PP_E}(\PP_I).$

By a translation of $-P$ in $K^n$, we can assume that
$\PP_E$ is a linear vector space: we are reduced to proving that, if $\tilde{f}: \PP_E \to K^m$ is an affine map and $\PP_I$ is a polyhedron in the vector space $\PP_E$ defined only by inequalities, then  $\tilde{f}(\PP_I)$ is a polyhedron.
This is the case thanks to Proposition \ref{prop:DIi} DI$_i$
and the theorem is proven.
\end{proof}

@@

\begin{proposition}[Characterization of polyhedra] \label{prop:carac}
    Non-empty polyhedra are image of polydiscs under a linear mapping.
\end{proposition}
\begin{proof}
    Let $\PP$ be a polyhedron in $K^n$. Then $\PP = \{x \in K^n : Ax+B \ge 0, Dx = e\}$ for some $A \in K^{d \times n}, b \in K ^d,  D\in  K^{m\times n}, e \in K^m$.

@@

If there exists $i_0 \in \{1,\ldots,n\}$ such that $s_{i_0} = 0$ then $\PP = f(D) = K$ and $\PP$ is a ball of infinite radius. Otherwise, we have $D = \{x \in K^n : x_i = \frac{b_i}{s_i} + O\left( \pi^{-val s_i} \right), i=1,\ldots,n \}$ and therefore for all $x \in  K$, $x \in P$ if and only if $x = a_0 + \sum_{i=1}^{n}( \frac{a_i b_i}{s_i} + O\left( \pi^{\val a_i - \val s_i} \right))= a_0  + \sum_{i=1}^{n} \frac{a_i b_i}{s_i} + O(\pi^d)$ where $d = \min \limits_{i = 1,\ldots,n} \val a_i - \val s_i$. Thus $\PP = \{x \in K : \val (x - a_0 - \sum_{i=1}^{n} \frac{a_i b_i}{s_i}) \ge d \}$ is a ball.

>>>>

Thanks to Definition \ref{smith_nf}, (the matrix of) $f$ can be written $f = Q^{-1} \Delta P$
with $P \in \GL_n(\OK),$ $Q \in \GL_m(\OK)$
and
$$
\Delta = \diag(\lambda_1, \ldots, \lambda_r, {\bf 0}_{\min(m,n)-r}) \in \mathrm{SNF}(f)\in \allmat_{n,m}(K)
$$
where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$ for
$\lambda_1,\dots,\lambda_r$ non-zero and $r \in \N.$

By Lemma \ref{lem:DIaut}, $\Qc = P(\PP)$ is a polyhedron defined only by inequalities.
We now prove that $\Delta (\Qc)$ is a polyhedron.
One can write that $\Delta$ is the composition
of the immersion 
$K^r \rightarrow K^n$
$(x_1,\dots,x_r)\mapsto (x_1,\dots,x_r,0,\dots,0),$ 
 the diagonal invertible mapping
$K^r \rightarrow K^r$,
$(x_1,\dots,x_r)\mapsto (\delta_1 x_1,\dots,\delta_r x_r)$,
and the projections
\begin{equation*}
  \begin{aligned}
    (x_1,\dots,x_{r+1}) &\mapsto (x_1,\dots,x_{r})   \\
    & \,\,\,\, \vdots \\
    (x_1,\dots,x_{n}) &\mapsto (x_1,\dots,x_{n-1}).
  \end{aligned}
\end{equation*}
%$(x_1,\dots,x_{r+1})\mapsto (x_1,\dots,x_{r}),$
%$(x_1,\dots,x_{r+2})\mapsto (x_1,\dots,x_{r+1}),$
%$\dots,$
%$(x_1,\dots,x_{n})\mapsto (x_1,\dots,x_{n-1}).$
Thus, thanks to Lemmas \ref{lem:DIimm}, \ref{lem:DIproj} and \ref{lem:DIaut},
$\Delta (\Qc)$ is a polyhedron. One can note that it is only when applying the
immersion as the last mapping in the composition chain that equalities are
needed to define the last polyhedron.

Finally, thanks to Lemma \ref{lem:DIaut},
$Q^{-1} \left( \Delta (\Qc) \right)$ is a polyhedron.
This concludes the proof.
\end{proof}

We can generalize from linear mappings to affine mappings.
\begin{proposition}[DI${}_i$]
Let $f : K^n \to K^m$ be an affine map and $\PP$ a polyhedron in $K^n$ defined only by inequalities.
Then $f(\PP)$ is a polyhedron. \label{prop:DIi}
\end{proposition}
\begin{proof}
  Let $v \in K^m$. One can see by immediate change
  of variables that $\Qc$ is a polyhedron in $K^m$ if and only if
  $\Qc+v$ is a polyhedron in $K^m$.
  Consequently, translating by $-f(O)$ in the codomain\footnote{Qu'est-ce q'est $O$ ? C'est $v$ ?},
  one can reduce to the case of Proposition \ref{prop:DIl}.
\end{proof}

@@

\begin{proof}[Proof of Theorem \ref{theo:DI}]
Recall that here $f : K^n \to K^m$ is an affine map and $\PP \subset K^n$ is a polyhedron.
Let us write $\PP = \PP_I \cap \PP_E$
with $\PP_I \coloneq \left\lbrace x \in K^n,  Ax+B \geq 0 \right\rbrace$
and $\PP_E \coloneq \left\lbrace x \in K^n,  Cx+D=0 \right\rbrace = v + \overrightarrow{\PP_E}.$
\footnote{c'est quoi le overrightarrow sur $\PP_E$ ?}
Then\footnote{je comprends pas la notation $f_{\PP_E}$.}
$f(\PP) = f_{\PP_E}(\PP_I).$

By a translation of $-v$ in $K^n$, we can assume that
$\PP_E$ is a linear vector space: we are reduced to proving that, if
$\tilde{f}: \PP_E \to K^m$ is an affine map and $\PP_I$ is a polyhedron in the vector space $\PP_E$ defined only by inequalities, then  $\tilde{f}(\PP_I)$ is a polyhedron.
This is the case thanks to Proposition \ref{prop:DIi}
and the theorem is proven.
\end{proof}

@@

\begin{proposition}[Characterization of polyhedra] \label{prop:carac}
    A non-empty polyhedron is the image of a polydisc under a linear mapping.
\end{proposition}
\begin{proof}
    Let $\PP$ be a polyhedron in $K^n$. Then $\PP = \{x \in K^n : Ax+B \ge 0, Dx = e\}$ for some $A \in K^{d \times n}, b \in K ^d,  D\in  K^{m\times n}, e \in K^m$.

@@

    If there exists $i_0 \in \{1,\ldots,n\}$ such that $s_{i_0} = 0$ then $\PP = f(D) = K$ and $\PP$ is a ball of infinite radius. Otherwise, we have
    $$
    D = \left\{x \in K^n : x_i = \frac{b_i}{s_i} + O\left( \pi^{-val s_i} \right), i=1,\ldots,n\right\}
    $$
    and therefore for all $x \in K$, one has $x \in P$ if and only if
    $$
    x = a_0 + \sum_{i=1}^{n}\left(\frac{a_i b_i}{s_i} + O( \pi^{\val a_i - \val s_i}) \right)
    = a_0  + \sum_{i=1}^{n} \frac{a_i b_i}{s_i} + O(\pi^d)
    $$
    where $d = \min \limits_{i = 1,\ldots,n} \val a_i - \val s_i$. Thus
    $\PP$ is the ball described by
    $$
    \PP = \{x \in K : \val (x - a_0 - \sum_{i=1}^{n} \frac{a_i b_i}{s_i}) \ge d \}.
    $$
\end{proof}
